\begin{abstract}\par
The company Algonauts Technologies Pvt. Ltd. specializes in developing Trading Solutions for the Indian Stock Market. Their products mainly deal with stocks entitled in National Stock Exchange \& Bombay Stock Exchange. They have wide-ranging products on automating stock trading decisions with the use of prediction algorithms. Adding to this they also develop customized trading platforms for  HNIs \& other Foreign-based clients. I worked as a Software Developer Intern in this firm.
\par


Due to the advent of Algorithmic Trading by SEBI dated April 03, 2008, providing a seamless way of Direct Market Access Facility to institutional Clients. 
In simple words, DMA allows authorized Brokers to carry out transactions that directly deals with stock exchanges. Therefore a registered client with valid credentials can carry out trading directly with stock exchange routed via brokers.  
This gave a wide spectrum of implementing various technologies on algorithmic trading. They are still on-going projects that directly deal with High-Frequency Trading Solutions, and it also made it possible to take advantage of algorithmic trading to all by providing trade calls generated through web-based platforms. 
\par



Our Product i.e. Mercury is a web-application based platform that enables a Client to deal with SELL\//BUY stocks in NSE. This product serves the functionality of seamless purchasing \& selling of the stocks over time. It has a devised set of algorithms executing in the back-end side that handles the live prediction of the stock prices. Initially, the product was design to serve the only specific client, on a specific aspect of the stock market. This became a barrier to up-scaling the product. Upscaling of the product demanded the need for authentication backend, business-subscription model, and performance upgrading. A basic, essential feature to have a scalable web-based product that will serve algorithmic trading calls for clients. For this purpose, we used Django 3 as a Web Development Framework which provided python-based backend to website. Used Kite Connect as a primary stockbroker to execute one-touch trade from the algonauts website itself. VueJs in frontend made products customizable according to endless user needs, which also optimized products for real-time calls and stock price delivery for WebSockets. 
\par

Adding to this, the Report not only confines to the assigned tasks that I have performed but also to the various suggestions/ improvements/ POCs that were later on implemented and successfully deployed.  
Constraints such as real-time  Data Fetching \& Rendering, we solved using Web Sockets. Order placing for purchasing \& selling is implemented using Kite connect which added convenient BUY / SELL. Thus assuring a real-time application with a convenient flow for users. Using lightweight Front end frameworks for seamless rendering enabled us to improvise the quality of our product keeping in mind the User Experience of a Typical Client/Trader. 
\par
This report will also serve as a benchmark for the technologies that were implemented for solving issues until now. That includes a highly dynamic admin customizable subscription model, Optimize UI with VueJs, Data consistency with Postgres, and secure and easily maintainable Django backend.
\end{abstract}
