\chapter{Results and Discussion}
Towards the end of internship our mercury web app and website was successfully deployed with added functionality.
\section{Achievement of Internship Objectives}

\tab The primary objective was to learn new technologies, development skills, understand business requirements, and apply them to develop a real-world application. This was possible under the guidance of Mr. Gaurav Mane. Not only technical skills were improved but also other soft skills such as communication between the team, discussions of project progress, online meets, etc.\\
\tab Algonauts also introduce to financial sector majorly regarding the stock market, and its working. Which helped me to frame stock market analysis to the problem of pattern extraction in terms of computer engineering \\
\tab Internship introduced me to the professional world, which gave me insights for practices followed in the IT sector and trained me to that level. Time management is one crucial practice learned with team collaboration been other.  


\section{Procurement of Industry Skills}
\tab I worked with Git version tracking and DevOps environment for project development, which is the standard mostly followed way for app development in collaborating teams. This made possible with continuous integration, testing in collaborating teams.\\
Along with technical skills I have also improvised in soft-skills like presentation, demonstration of ideas, and constructive discussion leading to project development.
Listing out the features and prioritizing them based on updating business needs which keeps development on track. And testing the crucial components rigorously.\\
\tab Also learned industry-standard for code writing, using licensed software, documenting the relevant code parts including functions, classes, and internal code lines if necessary are some of the skills accomplished over time.\\
\tab Keeping team members updated about my progress, collaborating with the marketing team to decide various plans, and devising the software accordingly.\\
\tab Using third parties libraries and integrating it into the current built app, was one of the most important technical skills acquired throughout the internship. Which gave me hands-on experience with UI libraries like JQuery, Vue, Vanilla Js, Webpush. And also got experienced for deploying platforms like Heroku and Azure Cloud

\section{Project Results}
A scalable web app (Mercury) and the website was developed. The website was deployed with additional features like authentication, subscription, user dashboard, and product dashboard. The product was deployed following the time constraints given.

The Mercury product is devised in such a way that any further addition/ modification will not affect the current functionality of the product, thus ensuring backward compatibility. All the work items were delivered on-time thus keeping the schedule intact. 

A proof of concept research work was done with certain bench-marking so that a better solution can be achieved. This was done for parameter optimization for the SuperTrend indicator for increased profit. The solution was achieved by analyzing the variation in profit on a single stock. And using adam optimizer, which optimized parameter for a black-boxed function which written profit.

\section{Challenges Tackled}
\begin{itemize}
    \item \textbf{On-Time} module delivery \& optimization, for both frontend and backend modules.
    
    \item \textbf{Grasping Financial Terms} The stock market technical analysis included various mathematical and statistical terms specifically related to it, like a candlestick, etc, which are the simple conditional mathematical equations.
    \item \textbf{Configurations \& migrations} Software versions difference lead to bugs in working code, so maintaining and keeping software version in sync, Git version control  solved the issues regarding tracking and forcing collaborator to use same versions of the software
  \item \textbf{Deploying Web App on Cloud} DevOps environment handles the majority of this issue with automation, but still while developing web apps, we missout on many aspects of the production environment. This once deployed we performed retesting web app and solving minor issues in the simulated production environment,

\end{itemize} 